# Tables {#sec-tables}

```{r}
#| results: "asis"
#| echo: false
source("_common.R")
status("complete")
```

## Introduction

In this chapter, you'll learn tools available table formats and style options.


### Prerequisites

In this chapter, some data is loaded from flat files / CSV in R with the **readr** package, which is part of the core tidyverse.

```{r}
#| label: setup
#| message: false

library(tidyverse)
```


## Basic Markdown Tables

|                  |  mpg| cyl| disp|  hp|
|:-----------------|----:|---:|----:|---:|
|Mazda RX4         | 21.0|   6|  160| 110|
|Mazda RX4 Wag     | 21.0|   6|  160| 110|
|Datsun 710        | 22.8|   4|  108|  93|
|Hornet 4 Drive    | 21.4|   6|  258| 110|
|Hornet Sportabout | 18.7|   8|  360| 175|
|Valiant           | 18.1|   6|  225| 105|

## Markdown Tables Alignment

| Default | Left | Right | Center |
|---------|:-----|------:|:------:|
| 12      | 12   |    12 |   12   |
| 123     | 123  |   123 |  123   |
| 1       | 1    |     1 |   1    |

: Demonstration of pipe table syntax


## Table from CSV Data

Here is what a simple CSV file looks like when loaded into a table

```{r}
#| label: tbl-students-table
#| echo: false
#| message: false
#| tbl-cap: Data from the students.csv file as a table.

read_csv("data/students.csv") |>
  knitr::kable()
```

::: {.callout-warning}
## Tip With Caption

This is an example of a callout with a caption.
The `Subtables` examples resulted in weird content within the PDF
:::

## Summary

- Overall, appears to work pretty well
- The `Subtables` examples resulted in weird content within the PDF

